Home

### 2016-05-03 analysis/index.Rmd
update index
add simulation from referee report

*  [Illustrate Zero Assumption](makefig_FDReg.html)
*  [Illustatrate dilution effect of low-precision observations](make_GOODPOOR_figs.html)
*  [Adaptive Shrinkage](adaptive_shrinkage.html)
*  [Comparing models: EE vs ET models](CompareEEvsETmodel.html)

>>>>

*  [Illustrate Zero Assumption](makefig_FDReg.html)
*  [Illustatrate dilution effect of low-precision observations](make_GOODPOOR_figs.html)
*  [Adaptive Shrinkage](adaptive_shrinkage.html)
*  [Comparing models: EE vs ET models](CompareEEvsETmodel.html)
*  [Checking how qvalue behaves in simulation suggested by referee](referee_uaza.html)
